\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
%\topmargin=-0.5in
\textheight=9.25in

\raggedright

%\pagenumbering{arabic}
\pagestyle{empty}

\def\bull{\vrule height 0.7ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[4]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip
			{#3}\\ \smallskip
			{#4}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}
\small
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
% \contact{Your Name}{http://www.yourname.com/}{you@youremailaddress.com}{(555) 555-5555}
\contact{GUANGLEI DAI}{Apt 902, 1411 Fort Street,
Montreal H3H 2N7}{TEL: (438) 877-6438~~ E-MAIL: guanglei.dai@mail.mcgill.ca}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objective
\smallskip
\header{Qualifications}
\begin{body}
	\begin{itemize} \itemsep -0pt  % reduce space between items
	\vspace{14pt}
	\item Rich experiences in interpreting ideas to software designs of scalable web and mobile frameworks. \\
	\medskip
	\item Dedicated to object-oriented software design patterns and modern software development methodology.\\
	\medskip
	\item Consistently delivers high quality softwares that meet the standards.
	\end{itemize}
\end{body}
\smallskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Experience
\header{Working Experiences}
\begin{body}
	\vspace{14pt}
	\textbf{Lead Software Engineer}---Nuance Communiations, Montreal, Canada  \hfill \emph{Mar.2016 - Present}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Lead a team of software developers and quality assurance engineers to build applications for industry users.
		\item Directed team meetings to verify progress and plan code direction.
		\item Architecture and review the code base to follow an easily scalable structure.
		\item Assigned coding and test automations tasks to various team members.
	\end{itemize}
	\vspace{14pt}
	\textbf{Software Engineer}---Nuance Communiations, Montreal, Canada  \hfill \emph{Oct. 2015 - Feb.2016}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Built a mobile voicemail to text SDK for telecommunication carriers with millions of users.
		\item Was responsible for quality of applications delivered for customer orders.
	\end{itemize}
	
	\vspace{14pt}
	\textbf{Fullstack Software Engineer}---Fans Entertainment Inc.(Acquired), Montreal, Canada  \hfill \emph{Mar. 2014 - Sep.2015}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Designed and implemented a well-known responsive and scalable venue management framework from Server BackEnd modelling, web FrontEnd management software to IOS framework and Android library.
		\item Created a real-time guest service platform within a mobile framework from scratches, serving national hockey league venues, Formula one games and commercial shows. Users' count range from 25,000 to 50,000 per event.
		\item Integrated customizable push notification service into a framework, sending messages to more than 100,000 mobile devices per event.
		\item Integrated major social medias and third-party's authentications, authorizations and content-fetching.
		\item Stepped in on 3 projects that were running behind schedule and shipped them on-time.
		\item Joined the start-up company when it had only five developers.
	\end{itemize}

	\textbf{Software Engineer}---Quebec Center For Biodiversity Science, Montreal, Canada  \hfill \emph{Jan. 2012 - Jan. 2014}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Refactored database structure to follow object-oriented design.
		\item Created mechanisms to detect spamming information and block harmful data.
	\end{itemize}	
	
	\textbf{Research Assistant}---McGill University, Montreal, Canada  \hfill \emph{Sep. 2011 - Dec. 2013}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
\item Proposed wireless relay networks with supervised learning detectors, which overcomes the limitation of conventional differential detection employed in multi-relay wireless networks over fast-fading environments. 
\item Performed Monte-Carolo simulations on the proposed schemes with \textbf{C} and Matlab.
	\end{itemize}

	\textbf{Mobile Developer Intern}---Zhongshu Health-Tech Limited, Shanghai, China \hfill \emph{Jan. 2010 - May, 2011}\\
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Developed portable blogger in JavaME.
	\end{itemize}
\end{body}
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Publications}
\begin{body}
	\vspace{14pt}
	G. Dai and H. Leib, "Detect-and-Forward Multirelay Systems With Decision-Feedback Differential Coherent Receivers," in IEEE Transactions on Wireless Communications, vol. 15, no. 2, pp. 1267-1281, Feb. 2016.
doi: 10.1109/TWC.2015.2487974
\end{body}
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Professional Certifications}
\begin{body}
	\vspace{14pt}
	\textbf{Xamarin-certified Mobile developer} \hfill \emph{Mar. 2016}\\
\end{body}
\smallskip

% Education
\header{Educations}
\begin{body}
	\vspace{14pt}
	\textbf{Master of Engineering, McGill University} {Montreal, Canada}. GPA 3.85  \hfill \emph{Sep. 2011 - Dec. 2013}{}  \\
	\textbf{Major:} Electrical and Computer Engineering \\
	\emph{Awards:} Graduate Excel Fellowship(Two times)\\

  \medskip	  
	\textbf{Bachelor of Science, Shanghai JiaoTong University} {Shanghai, China}   \hfill \emph{Sep. 2007 - Jun. 2011} \\
	\textbf{Major:} Electrical and Computer Engineering ~~~~~ \\
\end{body}
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Technical Tools}
\begin{body}
	\vspace{14pt}
	\emph{\textbf{Programming:}}{} XCode, Objective C, Xamarin, Android Studio, Java, Ruby on Rails, C\#, C/C++, SQL, ReactJS, React-Flux, Javascript, AJAX, REST API, JSON, HTML, CSS, AWS, Heroku, CodeShip, Git, Matlab, Monte Carlo simulations, \LaTeX\\
\medskip
	\emph{\textbf{Operating Systems:}}{} OS X, Linux, Windows\\
\end{body}
\smallskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Languages}
\begin{body}
	\vspace{14pt}
	English \& Chinese(fluent), French (Working Proficiency)\\
\end{body}
\smallskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document} 